---
title: "PracTools Project"
author: "Chia Wen Cheng and Mingqian Zheng"
date: "3/22/2024"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{bbm}
- \usepackage{setspace}
- \singlespacing
number_sections: yes
fontsize: 12pt
---
  
  
```{r setup, include=FALSE, tidy=TRUE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE, 
                      autodep=TRUE, cache.comments=FALSE,
                      message=FALSE, warning=FALSE)
```



```{r, echo=FALSE}
library(ggplot2)  
library(tidyverse)
library(dplyr)
library(glue)
library(tigris)
library(sf)
library(leaflet)
library(tidycensus)
library(readxl)
library(writexl)
library(sampling)
library(PracTools)
options(tigris_class = "sf")
options(tigris_use_cache = T)
set.seed(-1234)
```


```{r}
library(readxl)
data_initial <- read_excel("PrinceGeorgeMD.xlsx", sheet=2)
```


```{r}
data_initial <- data_initial %>%
  arrange(BlockGroup) %>%
  mutate(Tract = substr(BlockGroup, 1, nchar(BlockGroup) - 1),
         BlockGroupID = as.numeric(substr(BlockGroup, nchar(BlockGroup), nchar(BlockGroup))))
```

```{r}
PG_tract <- tracts(state="MD", county="Prince", year=2020)
PG_tract_trans <- st_transform(PG_tract,
"+proj=longlat +datum=WGS84")

PG_bg <- block_groups(state="MD", county="Prince", year=2020)
PG_bg_trans <- st_transform(PG_bg, "+proj=longlat +datum=WGS84")
```


### Filter out tracts with only 1 block group 

```{r}
tract_counts <- data_initial %>%
  group_by(Tract) %>%
  summarize(Count = n()) %>%
  filter(Count == 1) %>%
  ungroup()

single_block_groups <- data_initial %>%
  inner_join(tract_counts, by = "Tract")

# single_block_groups

single_tract_IDs <- single_block_groups$BlockGroup

single_tract <- PG_bg_trans %>%
  filter(GEOID %in% single_tract_IDs)

# single_tract
```

### check the map to make sure the block groups we will combine are geographically close

```{r}
leaflet() %>%
  addTiles() %>%
  addPolygons(data=PG_tract_trans,
              popup = ~NAME,
              fillOpacity = 0,
              fillColor= "snow") %>%
  addPolygons(data=PG_bg_trans,
              popup = ~GEOID,
              color = "black",
              weight = 1,
              opacity= 1,
              smoothFactor = 1,
              fillOpacity = 0,
              fillColor= "snow") %>%
  addPolygons(data=single_tract,
              color='yellow',
              popup = ~GEOID,
              weight=1, 
              fillOpacity = 1,
              fillColor="yellow")
              
```


### Update the dataset by combining single-block-group tracts to nearest tracts around

```{r}
data <- read_excel("PrinceGeorgeMD_modified.xlsx", sheet = 2) 

data <- data %>% 
  na.omit() %>%
  mutate(Tract = substr(BlockGroup, 1, nchar(BlockGroup) - 1), .before = BlockGroup)
```

```{r}
dim(data)
```


### Assign composite MOS 

```{r}
# number of total PSUs
M <- data %>% 
  group_by(Tract) %>% 
  summarise(n = n_distinct(Tract))
M <- sum(nrow(M)) ## 204 Tracts

# number of PSUs that will be selected
m <- 15 

# number of SSUs in PSU i
N_i <- data %>% 
  group_by(Tract) %>% 
  unique() %>% 
  count()

# number of SSUs that will be selected in PSU i
n_i <- 1 ## we should sample 1 block group from every PSU sampled

# number of total SSUs
N <- sum(N_i$n) ## 538 Block Groups

  
# total expected sample size for each domain across PSUs and SSUs considering non-response weighting
target <- data.frame(Age_Group= c("18-44", "45-64", "65+"), 
                     n = c(100, 100, 100), 
                     RR = c(0.6, 0.7, 0.85))
target <- target %>%
  mutate(n_weighted = n / RR)
target$n_weighted

# total expected sample size
n_sum <- sum(target$n_weighted) ## 427.170868
n_sum

# expected sample size across domain within each PSU selected
q_avg <- n_sum/m
q_avg ## 28.47805

# expected sample size for each domain across PSUs selected
n_avg <- n_sum/15 ## changed from n_sum/3 to n_sum/15 
n_avg
```

```{r}
calculate_age_groups <- function(data, group_var) {
  # Define the age categories and corresponding columns
  age_categories <- list(
    age_18 = c('Male18to19Yrs', 'Male20Yrs', 'Male21Yrs', 'Male22to24Yrs', 'Male25to29Yrs', 'Male30to34Yrs', 'Male35to39Yrs', 'Male40to44Yrs', 
            'Female18to19Yrs', 'Female20Yrs', 'Female21Yrs', 'Female22to24Yrs', 'Female25to29Yrs', 'Female30to34Yrs', 'Female35to39Yrs', 'Female40to44Yrs'),
    age_45 = c('Male45to49Yrs', 'Male50to54Yrs', 'Male55to59Yrs', 'Male60to61Yrs', 'Male62to64Yrs', 
            'Female45to49Yrs', 'Female50to54Yrs', 'Female55to59Yrs', 'Female60to61Yrs', 'Female62to64Yrs'),
    age_65 = c('Male65to66Yrs', 'Male67to69Yrs', 'Male70to74Yrs', 'Male75to79Yrs', 'Male80to84Yrs', 'MaleGE85Yrs', 
            'Female65to66Yrs', 'Female67to69Yrs', 'Female70to74Yrs', 'Female75to79Yrs', 'Female80to84Yrs', 'FemaleGE85Yrs')
  )

  # Determine the prefix based on the grouping variable
  prefix <- if (group_var == 'Tract') 'Qi' else 'Qij'

  # Perform the grouping and mutation
 result <- data %>%
   group_by(!!sym(group_var)) %>%
   mutate(
     across(all_of(unlist(age_categories)), ~sum(.x, na.rm = TRUE), .names = "{.col}"),
     "{prefix}_18" := sum(!!!syms(age_categories$age_18), na.rm = TRUE),
     "{prefix}_45" := sum(!!!syms(age_categories$age_45), na.rm = TRUE),
     "{prefix}_65" := sum(!!!syms(age_categories$age_65), na.rm = TRUE)) %>%
   mutate("{prefix}" := !!sym(paste0(prefix, "_18")) + !!sym(paste0(prefix, "_45")) + !!sym(paste0(prefix, "_65"))) %>%
   select(!!sym(group_var), !!sym(paste0(prefix)), !!sym(paste0(prefix, "_18")), !!sym(paste0(prefix, "_45")), !!sym(paste0(prefix, "_65"))) %>%
   unique()

  return(result)
}
```


```{r}
bg_data <- calculate_age_groups(data, 'BlockGroup') %>%
  mutate(Tract = substr(BlockGroup, 1, nchar(BlockGroup) - 1), .before = BlockGroup)
bg_data
```


```{r}
tract_data <- calculate_age_groups(data, 'Tract') 
tract_data
```


```{r}
Q <- sum(tract_data$Qi)
Q
```


```{r}
# number of total populations by domains across PSUs
Q_18 <- sum(tract_data$Qi_18)
Q_45 <- sum(tract_data$Qi_45)
Q_65 <- sum(tract_data$Qi_65)

# percentages for each domain and total domain population counts
target <- target %>%
  mutate(Q_d = c(Q_18, Q_45, Q_65),
         f_d = n_weighted / Q_d)
target$f_d*100 # f_d ()
target
```


```{r}
f_1 <- target$f_d[1]
f_2 <- target$f_d[2]
f_3 <- target$f_d[3]

# expected sample sizes for each domain in each PSU and selection probabilities
tract_data <- tract_data %>%
  mutate(S_i= Qi_18*f_1 + Qi_45*f_2 + Qi_65*f_3, # composite MOS for PSU i 
         S_i_18 = Qi_18*f_1,
         S_i_45 = Qi_45*f_2,
         S_i_65 = Qi_65*f_3,
         q_i_18 = n_avg*f_1*Qi_18/S_i,
         q_i_45 = n_avg*f_2*Qi_45/S_i,
         q_i_65 = n_avg*f_3*Qi_65/S_i)
         #pi_i_18 = m*S_i_18 / S_i, ## ?
         #pi_i_45 = m*S_i_45 / S_i,
         #pi_i_65 = m*S_i_65 / S_i) 

S_all <- sum(tract_data$S_i) ## 427.170868

# selection probability of each PSU
tract_data <- tract_data %>%
  mutate(pi_i = m*S_i/S_all)

tract_data[c("Tract","S_i", "q_i_18", "q_i_45", "q_i_65", "pi_i")]
```


```{r}
bg_data <- bg_data %>%
  mutate(S_ij = Qij_18*f_1 + Qij_45*f_2 + Qij_65*f_3, # composite MOS for SSU j at PSU i 
         qij_18 = q_avg*f_1*Qij_18/S_ij,
         qij_45 = q_avg*f_2*Qij_45/S_ij,
         qij_65 = q_avg*f_3*Qij_65/S_ij
         #pi_ij_18 = m*S_ij / sum(S_ij), ##
         #pi_ij_45 = m*S_ij / sum(S_ij),
         #pi_ij_65 = m*S_ij / sum(S_ij),
) 

# selection probability of each SSU
m_2 <- 1 
bg_data <- bg_data %>%
  left_join(tract_data %>% distinct(Tract, S_i), by = "Tract") %>% 
  mutate(pi_ij = m_2 * S_ij / S_i)
S_all_j <- sum(bg_data$S_ij)

bg_data
```

### find undersized block groups

```{r}
### quality control check 
# 1. qij_d* <= Qij(d)
undersized_bg <- bg_data %>%
  filter(qij_18 > Qij_18 | qij_45 > Qij_45 | qij_65 > Qij_65)
undersized_bg

# 2. q_avg <= Q_ij in every PSU 
any(q_avg > bg_data$Qij) # FALSE -> condition met 

# 3. n*q_avg <= Q_i+ in every SSU 
any(1*q_avg > tract_data$Qi) # FALSE -> condition met 

# 4. check selection prob <= 1 
# pi_i 
any(tract_data$pi_i > 1) # FALSE -> condition met

# pi_j|i 
# any(tract_data$pi_ji_18 > 1)
# any(tract_data$pi_ji_45 > 1)
# any(tract_data$pi_ji_65 > 1)
```

### check the tract the undersized block group is in

```{r}
bg_data %>% 
  filter(Tract == "24033801106")
```

$$\pi_i = m_{PSU} \frac{S_i}{S_+}, \quad \pi_{j|i} = m_{SSU} \frac{S_{j|i}}{S_i}, \quad \pi_{k|ij} (d) = \frac{q_{j|i}(d)}{Q_{j|i}(d)}$$ 



### combine the undersized block group with the next block group in its tract

```{r}
# data$BlockGroup[data$BlockGroup == "240338011061"] <- "240338011062"
```

### descriptive statistics of the final frame 

```{r}
frame_data <- read_excel("PrinceGeorgeMD_final.xlsx", sheet = 2) 

frame_data <- frame_data %>% 
  na.omit() %>%
  mutate(Tract = substr(BlockGroup, 1, nchar(BlockGroup) - 1), .before = BlockGroup)

## update tract data and bg data 
tract_data <- calculate_age_groups(data, 'Tract') %>%
  mutate(S_i= Qi_18*f_1 + Qi_45*f_2 + Qi_65*f_3, # composite MOS for PSU i 
         S_i_18 = Qi_18*f_1,
         S_i_45 = Qi_45*f_2,
         S_i_65 = Qi_65*f_3,
         q_i_18 = n_avg*f_1*Qi_18/S_i,
         q_i_45 = n_avg*f_2*Qi_45/S_i,
         q_i_65 = n_avg*f_3*Qi_65/S_i)

bg_data <- calculate_age_groups(frame_data, 'BlockGroup') %>%
  mutate(Tract = substr(BlockGroup, 1, nchar(BlockGroup) - 1), .before = BlockGroup,
         S_ij = Qij_18*f_1 + Qij_45*f_2 + Qij_65*f_3, # composite MOS for SSU j at PSU i 
         qij_18 = q_avg*f_1*Qij_18/S_ij,
         qij_45 = q_avg*f_2*Qij_45/S_ij,
         qij_65 = q_avg*f_3*Qij_65/S_ij)

```


```{r}
bg_data <- bg_data %>% 
  mutate(pi_ijk_18 = qij_18/Qij_18*100,
         pi_ijk_45 = qij_45/Qij_45*100,
         pi_ijk_65 = qij_65/Qij_65*100)

```



```{r}
summary(tract_data$S_i)
```

```{r}
summary(bg_data$S_ij)
```


```{r}
sum(tract_data$S_i)
```

```{r}
sum(bg_data$S_ij)
```


```{r, fig.width=6, fig.height=4}
combined_data <- rbind(
  data.frame(value = bg_data$S_ij, source = 'BG'),
  data.frame(value = tract_data$S_i, source = 'Tract')
)

ggplot(combined_data, aes(x = value, fill = source)) +
  geom_density(alpha = 0.5) +
  labs(x = "Value", y = "Density",
       fill = "Unit") +
  scale_fill_manual(values = c('BG' = 'blue', 'Tract' = 'red')) +
  theme(
    panel.background = element_rect(fill = "white", colour = "white"),  # Set panel background to white
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    axis.line = element_line(colour = "black"),  # Add axis lines
    legend.position = c(0.8, 0.8)
  )
```

# Sampling 

```{r}
# selection probability of each PSU
tract_data <- tract_data %>%
  mutate(pi_i = m*S_i/S_all)

# selection probability of each SSU
m_2 <- 1 
bg_data <- bg_data %>%
  left_join(tract_data %>% distinct(Tract, S_i), by = "Tract") %>% 
  mutate(pi_ij = m_2 * S_ij / S_i)
```

```{r}
sum(tract_data$pi_i)
```


## 1st stage - 15 PSU 
```{r}
pik <- inclusionprobabilities(tract_data$pi_i, 15)
psu_s=UPsystematic(pik)
selected_psu <- which(psu_s==1)
selected_psu
selected_psu_data <- getdata(tract_data, psu_s)
selected_psu_data ## the combined block group was not selected
```

## 2nd stage - sample BG 

```{r}
bg_data_selected_psu <- bg_data %>%
  filter(Tract %in% selected_psu_data$Tract)
verify_15_psu <- bg_data_selected_psu %>% 
  group_by(Tract) %>% 
  summarise(n = n_distinct(Tract))
verify_15_psu <- sum(nrow(verify_15_psu)) ## 15

# Get unique Tract values
unique_tracts <- unique(bg_data_selected_psu$Tract)

# Create an empty list to store the subsets
tract_data_list <- list()

# Iterate over each unique Tract
for (tract_value in unique_tracts) {
  # Subset block groups for the current Tract
  subset_data <- subset(bg_data_selected_psu, Tract == tract_value)
  
  # Store the subset data frame in the list
  tract_data_list[[paste0("Tract_", tract_value)]] <- subset_data
}


# Create an empty list to store the results for each Tract
results_list <- list()

# Iterate over each subset data frame
for (i in seq_along(tract_data_list)) {
  # Get the subset data frame
  subset_data <- tract_data_list[[i]]
  
  # Calculate inclusion probabilities
  pik_bg <- inclusionprobabilities(subset_data$pi_ij, 1)
  
  # Generate systematic sampling
  ssu_s <- UPsystematic(pik_bg)
  
  # Get selected SSU indices
  selected_ssu <- which(ssu_s == 1)
  
  # Get data for selected SSUs
  selected_ssu_data <- getdata(subset_data, ssu_s)
  
  # Store the results in the list
  results_list[[i]] <- list(
    pik_bg = pik_bg,
    ssu_s = ssu_s,
    selected_ssu = selected_ssu,
    selected_ssu_data = selected_ssu_data
  )
}

selected_ssu_data <- data.frame()

# Loop through each element in the results_list
for (i in seq_along(results_list)) {
  # Append the subset dataframe to selected_ssu_data
  selected_ssu_data <- rbind(selected_ssu_data, results_list[[i]]$selected_ssu_data)
}

selected_ssu_data

write_xlsx(selected_ssu_data, "sample.xlsx")
```

### check selected units and characteristics

```{r}
selected_characteristics <- frame_data %>% 
  filter(BlockGroup %in% selected_ssu_data$BlockGroup)
selected_characteristics <- selected_characteristics[, -c(3:10, 30:34)]
selected_characteristics <- selected_characteristics %>% 
  mutate(age_18_male = rowSums(selected_characteristics[c("Male18to19Yrs", "Male20Yrs", "Male21Yrs", "Male22to24Yrs", "Male25to29Yrs", "Male30to34Yrs", "Male35to39Yrs", "Male40to44Yrs")])) %>% 
  mutate(age_45_male = rowSums(selected_characteristics[c("Male45to49Yrs", "Male50to54Yrs", "Male55to59Yrs", "Male60to61Yrs", "Male62to64Yrs")])) %>% 
  mutate(age_65_male = rowSums(selected_characteristics[c("Male65to66Yrs", "Male67to69Yrs", "Male70to74Yrs", "Male75to79Yrs", "Male80to84Yrs", "MaleGE85Yrs")])) %>%
  mutate(age_18_female = rowSums(selected_characteristics[c("Female18to19Yrs", "Female20Yrs", "Female21Yrs", "Female22to24Yrs", "Female25to29Yrs", "Female30to34Yrs", "Female35to39Yrs", "Female40to44Yrs")])) %>% 
  mutate(age_45_female = rowSums(selected_characteristics[c("Female45to49Yrs", "Female50to54Yrs", "Female55to59Yrs", "Female60to61Yrs", "Female62to64Yrs")])) %>% 
  mutate(age_65_female = rowSums(selected_characteristics[c("Female65to66Yrs", "Female67to69Yrs", "Female70to74Yrs", "Female75to79Yrs", "Female80to84Yrs", "FemaleGE85Yrs")]))

selected_characteristics <- selected_characteristics %>%
  mutate(percentage = select(selected_characteristics, starts_with("age_")) / rowSums(select(selected_characteristics, starts_with("age_"))) * 100)

selected_characteristics_long <- selected_characteristics %>%
  pivot_longer(cols = starts_with("age_"), 
               names_to = "AgeGenderGroup", 
               values_to = "Count") %>%
  group_by(BlockGroup) %>%
  mutate(percentage = Count / sum(Count) * 100)

selected_characteristics_long
# selected_characteristics

# Plot
ggplot(selected_characteristics_long, aes(x = BlockGroup, y = percentage, fill = AgeGenderGroup)) +
  geom_bar(position = "stack", stat = "identity") +
  labs(x = "Selected Block Groups",
       y = "Percentage") +
  scale_fill_manual(values = c("age_18_male" = "blue", "age_45_male" = "orange", "age_65_male" = "red", "age_18_female" = "lightblue", "age_45_female" = "yellow", "age_65_female" = "pink"),
                    name = "Age and Gender Groups",
                    labels = c("Female age 18-44", "Male age 18-44", "Female age 45-64", 
               "Male age 45-64", "Female age 65+", "Male age 65+")) +
  theme_minimal() + 
  coord_flip()

```


### check self-weighting

```{r}
check <- selected_ssu_data %>%
  select(Tract, BlockGroup, pi_ij, pi_ijk_18, pi_ijk_45, pi_ijk_65) %>%
  mutate(f_18 = target$f_d[1]*100,
         f_45 = target$f_d[2]*100,
         f_65 = target$f_d[3]*100) 
check <- check %>% 
  mutate(pi_i = tract_data %>% 
           filter(Tract %in% check$Tract) %>% 
           pull(pi_i))


round(check$f_18, 4) == round(check$pi_i*check$pi_ij*check$pi_ijk_18, 4)
## True
round(check$f_45, 4) == round(check$pi_i*check$pi_ij*check$pi_ijk_45, 4)
## True
round(check$f_65, 4) == round(check$pi_i*check$pi_ij*check$pi_ijk_65, 4)
## True
```

### 7. Map

#### a. Prince George's County

```{r}
# Tracts and Block Groups
leaflet() %>%
  addTiles() %>%
  addPolygons(data=PG_tract_trans,
              popup = ~NAME,
              fillOpacity = 0,
              fillColor= "snow") %>%
  addPolygons(data=PG_bg_trans,
              popup = ~paste("BG", GEOID),
              color = "black",
              weight = 1,
              opacity= 1,
              smoothFactor = 1,
              fillOpacity = 0,
              fillColor= "snow")
```


#### b. Selected Tracts and Block Groups

```{r}
selected_psu_data <- selected_psu_data %>% 
  left_join(N_i %>% distinct(Tract, n), by = "Tract")

selcted_psu_IDs <- selected_psu_data$Tract

selected_psu_geodata <- PG_tract_trans %>%
  filter(GEOID %in% selcted_psu_IDs)

selected_ssu_IDs <- selected_ssu_data$BlockGroup
selected_ssu_geodata <- PG_bg_trans %>%
  filter(GEOID %in% selected_ssu_IDs)

```



```{r}
leaflet() %>%
  addTiles() %>%
  addPolygons(data = PG_tract_trans,
              popup = ~NAME,
              color = "forestgreen",
              opacity = 1, 
              fillOpacity = 0,
              fillColor= "snow") %>%
  addPolygons(data=PG_bg_trans,
              popup = ~paste("Block Group", GEOID),
              color = "black",
              weight = 1,
              opacity= 1,
              smoothFactor = 1,
              fillOpacity = 0,
              fillColor= "snow") %>%
  # Selected Tracts
  addPolygons(data = selected_psu_geodata,
              color='orange',
              popup = ~paste("Sampled", "<br>", "Tract", GEOID), 
              weight = 1, 
              fillOpacity = 0.5,
              fillColor="orange") %>% 
  # Selected Block Groups
  addPolygons(data = selected_ssu_geodata,
              color ='darkorange',
              popup = ~paste("Sampled", "<br>", "Block Group", GEOID), 
              weight = 0.7, 
              fillOpacity = 1,
              fillColor = "darkorange")
              
```

## make deliverables 2 and 3

```{r}
## Text files giving the units used for the area frame and relevant census counts and measures of size [filename: FRAME#_GROUPNAME.pdf]

FRAME_ChiaWen_Mingqian <- frame_data %>% 
  select('Tract', 'BlockGroup', 'NAME', 'Male18to19Yrs', 'Male20Yrs', 'Male21Yrs', 'Male22to24Yrs', 'Male25to29Yrs', 'Male30to34Yrs', 'Male35to39Yrs', 'Male40to44Yrs', 
            'Female18to19Yrs', 'Female20Yrs', 'Female21Yrs', 'Female22to24Yrs', 'Female25to29Yrs', 'Female30to34Yrs', 'Female35to39Yrs', 'Female40to44Yrs',
    'Male45to49Yrs', 'Male50to54Yrs', 'Male55to59Yrs', 'Male60to61Yrs', 'Male62to64Yrs', 
            'Female45to49Yrs', 'Female50to54Yrs', 'Female55to59Yrs', 'Female60to61Yrs', 'Female62to64Yrs',
    'Male65to66Yrs', 'Male67to69Yrs', 'Male70to74Yrs', 'Male75to79Yrs', 'Male80to84Yrs', 'MaleGE85Yrs', 
            'Female65to66Yrs', 'Female67to69Yrs', 'Female70to74Yrs', 'Female75to79Yrs', 'Female80to84Yrs', 'FemaleGE85Yrs') %>% 
  left_join(tract_data, frame_data, by = 'Tract')
  
write_xlsx(FRAME_ChiaWen_Mingqian, "FRAME_Chia Wen+Mingqian.xlsx")

## Text file for the selected sample along with relevant census counts, measures of size, selection probabilities, and weights [filename: SAMPLE_GROUPNAME.pdf]

SAMPLE_ChiaWen_Mingqian <- frame_data %>% 
  select('Tract', 'BlockGroup', 'NAME', 'Male18to19Yrs', 'Male20Yrs', 'Male21Yrs', 'Male22to24Yrs', 'Male25to29Yrs', 'Male30to34Yrs', 'Male35to39Yrs', 'Male40to44Yrs', 
            'Female18to19Yrs', 'Female20Yrs', 'Female21Yrs', 'Female22to24Yrs', 'Female25to29Yrs', 'Female30to34Yrs', 'Female35to39Yrs', 'Female40to44Yrs',
    'Male45to49Yrs', 'Male50to54Yrs', 'Male55to59Yrs', 'Male60to61Yrs', 'Male62to64Yrs', 
            'Female45to49Yrs', 'Female50to54Yrs', 'Female55to59Yrs', 'Female60to61Yrs', 'Female62to64Yrs',
    'Male65to66Yrs', 'Male67to69Yrs', 'Male70to74Yrs', 'Male75to79Yrs', 'Male80to84Yrs', 'MaleGE85Yrs', 
            'Female65to66Yrs', 'Female67to69Yrs', 'Female70to74Yrs', 'Female75to79Yrs', 'Female80to84Yrs', 'FemaleGE85Yrs') %>%
  filter(BlockGroup %in% selected_ssu_data$BlockGroup) %>% 
  left_join(selected_ssu_data, frame_data, by = 'BlockGroup')

write_xlsx(SAMPLE_ChiaWen_Mingqian, "SAMPLE_Chia Wen+Mingqian.xlsx")
```


## Precision Anticipation


```{r}
simulate_target <- bg_data %>%
  left_join(tract_data %>% distinct(Tract, pi_i), by = "Tract") %>%
  select("Tract", "BlockGroup", "Qij", "pi_i", "pi_ij")
simulate_data <- simulate_target[rep(seq_len(nrow(simulate_target)), simulate_target$Qij), ]
```

```{r}
probabilities <- c(0.3, 0.6, 0.9)

# Simulate y values for each proportion
for (p in probabilities) {
  column_name <- paste("y", p * 10, sep = "")
  simulate_data[[column_name]] <- rbinom(nrow(simulate_data), 1, p)
}
```


```{r}
simulate_data
```


```{r}
pp.tract <- table(simulate_data$Tract) / nrow(simulate_data)
  
precision_df <- round(rbind(y3=BW3stagePPS(X=simulate_data$y3, pp=pp.tract,
                           psuID=simulate_data$Tract, ssuID=simulate_data$BlockGroup),
            y6=BW3stagePPS(X=simulate_data$y6, pp=pp.tract,
                           psuID=simulate_data$Tract, ssuID=simulate_data$BlockGroup),
            y9=BW3stagePPS(X=simulate_data$y9, pp=pp.tract,
                           psuID=simulate_data$Tract, ssuID=simulate_data$BlockGroup)),
      digits=4)

precision_df <- as.data.frame(precision_df)
```

```{r}
precision_df
```



```{r}
precision_df <- precision_df %>%
  mutate(relvar = `unit relvar` / (15*1*q_avg) * (k1*delta1*1*q_avg + k2*(1+delta2*(q_avg-1))))

precision_df
```


$$relvar(\hat{t}_{pwr})=\frac{V(\hat{t}_{pwr})}{t^2_U} = \frac{B^2}{m}+\frac{W^2_2}{m\bar n}+ \frac{W^2_3}{m\bar{n}\bar{\bar{q}}} = \frac{\tilde{V}}{m\bar{n}\bar{\bar{q}}} \{ k_1\delta_1\bar{n}\bar{\bar{q}}+k_2[1+\delta_2(\bar{\bar{q}}-1)]\} $$

## Variance Estimation 

$$Var(\hat{\theta}_d) = \frac{1}{R}\sum_{r=1}^R (\hat{\theta}_{r,d}-\hat{\theta}_d)^2$$

$$Total\:Variance= \sum_{d=1}^D Var(\hat{\theta}_d)$$







